Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Move scale mismatch phrase from abstract to intro

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (often
    vertical-axis) turbines depend on many parameters: solidity, blade profile,
    blade pitch, number of blades, strut drag, operational parameters such as tip
    speed ratio---and Reynolds number. Experiments were performed with a large
    laboratory-scale high solidity cross-flow turbine to investigate Reynolds number
    effects on performance and wake transport characteristics. A key question was
    what an acceptable Reynolds number mismatch is for scaled physical model tests
    of cross-flow turbines, both from the perspective of predicting full scale
    performance and flow dynamics, as well as numerical model validation. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}

@@

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however,
there still is concern at which scale an experiment must be performed to be
relevant to full-scale application. Similarly, it is questionable whether
numerical models validated with physical model data obtained orders of magnitude
away from prototype scale should be considered validated at all.

@@

At lower Reynolds numbers we observed lower levels of turbulence in the wake at
$x/D=1$, along with lower levels of turbulent transport with respect to mean
streamwise momentum and mean kinetic energy recovery in the streamwise
direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$, which may be due to larger
free surface deformation reducing the near-wake's cross-sectional area. Despite
being order of magnitude smaller than other transport processes, viscous
diffusion increased rapidly with decreasing $Re$, and is expected to become
significant to the wake dynamics around $Re_D \sim 10^4$. Overall, the total
wake transport measured leveled off at essentially the same Reynolds number that
the performance did.

>>>>

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (often
    vertical-axis) turbines depend on many parameters: solidity, blade profile,
    blade pitch, number of blades, strut drag, operational parameters such as tip
    speed ratio---and Reynolds number. Experiments were performed with a large
    laboratory-scale high solidity cross-flow turbine to investigate Reynolds number
    effects on performance and wake characteristics. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}

@@

With regards to wind and marine hydrokinetic (MHK) turbines, scaled physical
models are used to validate predictive numerical models, predict full-scale
performance of individual turbines, and design or investigate arrays of devices.
Scaled models have the benefit of being significantly less expensive, however, a
key question is whether or not an acceptable scale mismatch exists. Similarly,
it is questionable whether numerical models validated with physical model data
obtained orders of magnitude away from prototype scale should be considered
validated at all.

@@

At higher Reynolds numbers we observed lower levels of turbulence in the wake at
$x/D=1$, along with lower levels of turbulent transport with respect to mean
streamwise momentum and mean kinetic energy recovery in the streamwise
direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$, which may be due to larger
free surface deformation reducing the near-wake's cross-sectional area. Despite
being order of magnitude smaller than other transport processes, viscous
diffusion increased rapidly with decreasing $Re$, and is expected to become
significant to the wake dynamics around $Re_D \sim 10^4$. Overall, the total
wake transport measured leveled off at essentially the same Reynolds number that
the performance did.
